---
title: "Stefan Laser's CV"
author: Stefan Laser
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{css, echo=FALSE}
/* Turn-off side-bar for publications */
.pagedjs_page:not(:nth-of-type(-n+5)) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
```

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1PAcxb7nRv3x4DDOFGpRXpM-gzXqtzmV2ZNOAkYB6kQY/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

<!-- include a fontawesome reference -->
<script src="https://kit.fontawesome.com/0a75c4d7c0.js" crossorigin="anonymous"></script>

Aside
================================================================================
<!--
```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```

```{r}
if(params$pdf_mode){
  cat("View this CV online with links at https://hightech-am-ende.de/cv.html")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://hightech-am-ende.de/cv.pdf)")
}
```
-->

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------
This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown) and [**datadrivencv**](http://nickstrayer.me/datadrivencv/index.html).

<!--
Code available on <i class="fa fa-github"></i>  [GitHub](https://github.com/LaserStefan/cv/). 
-->
Last updated on `r Sys.Date()`.



Main
================================================================================

Curriculum Vitae<br>Dr Stefan Laser {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------
::: aside
#### Programming and Software Skills
I have developed expertise in digital methods. Approaches like Controversy Mapping require data analysis techniques and programming skills. My skills and interests:
<!--
```{r}
CV %>% print_skill_bars()
```
-->

<i class="fa-brands fa-python fa-fw"></i> `Python: Data Science`

<i class="fab fa-r-project fa-fw"></i> `R: Data Science`

<i class="fa-solid fa-circle-nodes fa-fw"></i> `Gephi: Networks`

<i class="fa-solid fa-highlighter fa-fw"></i> `MaxQDA: Coding`

<i class="fab fa-markdown fa-fw"></i> `Markdown: Memos`


:::

```{r}
CV %<>% print_section('education')
```

Academic Work Experience {data-icon=address-card}
--------------------------------------------------------------------------------
::: aside
#### Memberships
```{r}
CV %<>% print_text_block('membership')
```
:::

```{r}
CV %<>% print_section('research_positions')
```

Funding and Grants {data-icon=address-card}
--------------------------------------------------------------------------------
::: aside
#### Language Skills
Starting with the 2019 appointment in Bochum, I have been employed in international contexts with English as the primary language.<br>

```{r}
CV %>% print_lang_bars()
```
::: 

```{r}
CV %<>% print_section('funding')
```


<!-- <div style="break-after:page"></div> {.page-break-before} -->



Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

::: aside
#### On Teaching
```{r}
CV %<>% print_text_block('teaching_experience_aside')
```
:::


```{r}
CV %<>% print_section('teaching_positions')
```

<!--

ABSTRACTS {data-icon=NULL .no-timeline .page-break-before}
--------------------------------------------------------------------------------

Selected publications {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section("selected_publications") 
```
-->

LIST OF PUBLICATIONS {data-icon=NULL .no-timeline .page-break-before}
--------------------------------------------------------------------------------

Monographs {data-icon=book} 
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('books')
```

Edited Volumes and Special Issues {data-icon=book}
--------------------------------------------------------------------------------
<!--
::: aside
```{r}
CV %<>% print_text_block('publication_aside')
```
:::
-->
```{r}
CV %<>% print_section('editorials')
```

Peer-Reviewed Articles {data-icon=file-text}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```

Book Chapters {data-icon=file-text-o}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('chapters')
```

Review-Articles and Other Texts {data-icon=newspaper-o}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('other_texts')
```


Selected Talks (All translated) {data-icon=microphone}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_talks')
```

<!--
```{r}
CV %<>% print_links()
```
-->

